\documentclass[12pt]{article}
\begin{document}

\title{ENG1030 - Opreational Amplifiers }
\date{7 August, 2012}
\author{Gordon Ng}
\maketitle

\pagebreak
\tableofcontents
\pagebreak
\section{Learning Objectives}
\begin{itemize}
\item Understand what an amplifier does.
\end{itemize}
\section{What is an amplifier?}
\begin{itemize}
\item Makes things bigger (Mostly voltages, currents, electrical powers)
\item The outpit should replicate the input waveform.
\end{itemize}
\subsection{How It Powers}
Due to conservation, the energy needed to amplify the signal comes from power supply( also known as \textbf{power rail}.)\\
The voltage are usualy fixed.
\subsection{Single and Dual-Rail Supplies}
\subsubsection{Dual Rail Supply}
They require two supply connected in series but they are great for high power applications.
\subsubsection{Single Rail Supply}
They can burn out speakers.
\section{Amplifier's Bandwidth}
Bandwidth roughly translates to how rapidly its out put can change.
A 20-khz audio amplier's output can change its voltage from positive to negative and back roughly 20,000 times per second.
\pagebreak
\section{Opreational Amplifiers}
It contains many integrated circuits.\\
It is the basis for many low-signal circuits.

\begin{itemize}
\item  Current is sourced from the positive supply when need to make the output voltage higher.
\item Current is sunk to the negative supply when needed to make the output voltage
\item Output Voltage:
\begin{displaymath}
V_o=A_{OL}(v_1-v_2)
\end{displaymath}
\item The input voltage must be within the range of supply rail voltage.
\item A supply bypass capacitors provides current when the current needs it. \textbf{Always Use Them!} It fills up energy when we don't use it and empties when we use ot.
\item Gain:
\begin{displaymath}
Gain=\frac{V_o}{V_s}
\end{displaymath}
\begin{displaymath}
V_{IN}=v_S{R_i}{R_i+R_s}
\end{displaymath}
\begin{displaymath}
V_{out}=\frac{A_oV_{IN}}{R_o+R_L}
\end{displaymath}

\begin{displaymath}
\end{displaymath}
\pagebreak
\section{Unity Gain Buffer}
\subsection{Purpose}
\item It can stop signals flowing in the wrong direction.
\item Its \textbf{gain is independent of source and load resistances}
\item It has a gain of 1. $V_{Out}=IN_+=IN_-=V_{IN}$
\subsection{Simple Circuit}
\item We take a connection out of output and feed it back to $V_-$
\subsection{Negative Feedback}
\subsection{Non-ideal analysis II}
\begin{displaymath}
\frac{V_o}{V_s}=\frac{1}{1+\frac{R_o}{R_O+A_OR_I}}
\end{displaymath}
\section{Ideal Operational Amplifier}
\item No currents flows into or out of the input.
\item The op-amp's internal volrage Gain,$A_O$ is infinite. Therefore $IN_+=IN_-$
\item The op-amp's response to $IN_+$ and $IN_-$ changing the same amount in the same direction is zero. This is called \textbf{common mode voltage gain}.
\item The op-amp's output is connected to a perfect (Voltage-controlled) power ssource that has zero impedence.
\item The op-amp is infinitely fast to respond to any change in input(infinite bandwidth_.
\end{itemize}
\end{document}